### 2024-08-21 ms.qmd
Updates

```{r, tbl-data}
#| label: tbl-data
#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"
source(here("R", "func.R"))
#
############################## MAKING THE TABLE ##############################
## Table format
set_flextable_defaults(
 font.family = "Times New Roman",
 fint.size = 10)
# Split the table_data df by task
real_table <- flextable(new_table_data) %>%
    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%
    set_table_properties(width = 1) %>%
    align(align="center", part="all") %>% 
    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
    set_header_labels(Mean_Associative = "Mean",
                      `95% CI_Associative` = "95% CI",
                      `p-value_Associative` = "p-value",
                      Mean_Reversal = "Mean",
                      `95% CI_Reversal` = "95% CI",
                      `p-value_Reversal` = "p-value") %>%
    italic(j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header
    autofit() 
real_table
```

@@

#### Treatments effects
Table S1.- statistical comparisson between treatments

Table S2.- Evaluating whether choice diff from 0.5 and interest diff from 0

@@

_Table S4. Number of individuals per treatment that chose the cricket oriente horizontally (Horizontal) or vertically (Vertical) in our control tests. p-value indicates the result of the binomial test comparing the number of choices between both choices._
```{r, tbl-orientation}
#| label: tbl-sides
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_or_res <- data_orient %>%
  mutate(choice_or = ifelse(choice_horizontal == 0, "Vertical", "Horizontal")) %>%
  dplyr::select(trt, choice_horizontal, choice_or) %>%
  group_by(trt) %>% # Group by treatment and test
  summarize(
    Horizontal_Count = sum(choice_or == "Horizontal"),
    Vertical_Count = sum(choice_or == "Vertical")
  ) %>% # Count the number of horizontal and vertical choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = Horizontal_Count + Vertical_Count,  # Calculate total choices
    p_value = format_dec(binom.test(Horizontal_Count, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(trt = recode(trt, 
            "B_23" = "CORT-Cold (n = 20)", 
            "A_23" = "Control-Cold (n = 20)", 
            "B_28" = "CORT-Hot (n = 20)", 
            "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, Horizontal_Count, Vertical_Count, p_value) %>% # Remove unused columns
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
orient_table <- flextable(data_or_res) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("Horizontal"), part = "header") %>%
  compose(j = 3, value = as_paragraph("Vertical"), part = "header") %>%
  compose(j = 4, value = as_paragraph("p-value"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
orient_table
```

>>>>

Include here general text: Results are in Table 1 and figure X.

Preliminary results showed: talk about sex and age, refer to summary (prepare that), and explain how did we control by that.

_Table 1. Estimates of the effects of each treatment and their interaction on the latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05._
```{r, tbl-data}
#| label: tbl-data
#| tbl-cap: "Estimates of the effects of each treatment and their interaction on the latency, choice, and interest shown for the higher amount of food in each of the numerical discrimination tests. The table shows the comparissons for each predictor and the p~mcmcm~ value of the comparissons. In bold, the estimates with p~mcmc~ < 0.05."
source(here("R", "func.R"))
#
# Making the df for each variable
#
## Initialize df_org as a list to store data frames for each variable
df_org <- list()
## Define variables and tests
variable <- c("Latency", "Choice", "Interest")
test <- c("1VS4", "1VS3", "2VS4", "2VS3", "3VS4")
## Loop over each variable
for(a in variable){
  # Select the original df to use depending on the variable
  if(a == "Latency"){
    post <- post_lat
  } else if(a == "Choice"){
    post <- prob_choice
  } else if(a == "Interest"){
    post <- post_int
  }
  df_tables <- data.frame()
  for(b in test){
    # Modify the df to get the values per each test
    post_mod <- post %>%
      dplyr::select(dplyr::matches(b))
    # Extract the required columns
    Cold_CORT <- post_mod[[paste0("X", b, "_Cold_CORT")]]
    Cold_Control <- post_mod[[paste0("X", b, "_Cold_Control")]]
    Hot_CORT <- post_mod[[paste0("X", b, "_Hot_CORT")]]
    Hot_Control <- post_mod[[paste0("X", b, "_Hot_Control")]]
    # Calculate effects and pmcmc values
    effect_temp <- format_dec(mean(c(Hot_CORT, Hot_Control)) - mean(c(Cold_CORT, Cold_Control)), 3)
    effect_hormone <- format_dec(mean(c(Hot_Control, Cold_Control)) - mean(c(Hot_CORT, Cold_CORT)), 3)
    interaction <- format_dec((mean(Hot_Control) - mean(Cold_Control)) - (mean(Hot_CORT) - mean(Cold_CORT)), 3)
    #
    pmcmc_temp <- format_p(pmcmc(c(Hot_CORT, Hot_Control) - c(Cold_CORT, Cold_Control)), 3)
    pmcmc_hormone <- format_p(pmcmc(c(Hot_Control, Cold_Control) - c(Hot_CORT, Cold_CORT)), 3)
    pmcmc_interaction <- format_p(pmcmc((Hot_Control - Cold_Control) - (Hot_CORT - Cold_CORT)), 3)
    # Define labels and values
    effects_predictors_names <- c("Temperature", 
                          "Hormone", 
                          "Interaction")
    values_predictors <- c(effect_temp, effect_hormone, interaction)
    values_pmcmc <- c(pmcmc_temp, pmcmc_hormone, pmcmc_interaction)
    # Create a temporary data frame for this loop iteration
    temporal_df <- data.frame(Predictor = effects_predictors_names,
                        Effect = values_predictors,
                        pmcmc = values_pmcmc,
                        Test = b,
                        stringsAsFactors = FALSE)
    # Merge the temporary data frame to the main df_tables
    df_tables <- rbind(df_tables, temporal_df)
  }
  df_tables$Variable <- a
  df_org[[a]] <- df_tables
}
# Combine all data frames in df_org into one data frame
table_df <- do.call(rbind, df_org)
# Convert the combined list into a data frame and modify for the table
table_df <- as.data.frame(table_df, stringsAsFactors = FALSE) %>%
  mutate(results = paste(Effect, "(p", pmcmc, ")")) %>%
  dplyr::select(Variable, Test, Predictor, results) %>%
  pivot_wider(names_from = Test, values_from = c(results), names_prefix = "")
#
#
# Making the table
#
## Table format
set_flextable_defaults(
 font.family = "Arial",
 fint.size = 10)
# Split the table_data df by task
real_table <- flextable(table_df) %>%
    set_table_properties(width = 1) %>%
    align(align="center", part="all") %>% 
    add_header_row(values = c("", "Tests"), colwidths = c(2, 5)) %>%
    flextable::compose(i = c(2,3,5,6,8,9), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = c(3,6), j = c(1:7), part = "body") %>% # To make some horizontal lines
    vline(i = (1:9), j = c(2:6), part = "body") %>% # To make some vertical lines on body
    vline(i = 2, j=c(2:6), part = "header") %>% # To make some vertical lines on header
    autofit() 
real_table

Results: Latency, Choice, and Interest for each test and treatment, references to fig x and Table 1. Basically, no effects of treatment on the performance of the numerical discrimination task. no discrimination either (refer to Table in Suppl. Material).

```{r, fig-results}
#| label: fig-results
#| fig.cap: "" 
```

@@

#### Preliminary results

_Table S1.- Summary of the model_

```{r, tbl-summary}
#| label: tbl-summary
#| tbl-cap: "Summary of the model fitted to the data."
```

#### Treatments effects

_Table S2.- Evaluating whether choice diff from 0.5 and interest diff from 0_
```{r, tbl-summary}
#| label: tbl-summary
#| tbl-cap: "Summary of the model fitted to the data."
```

@@

_Table S4. Number of individuals per treatment that chose the cricket oriente horizontally (Horizontal) or vertically (Vertical) in our control tests. p-value indicates the result of the binomial test comparing the number of choices between both choices._
```{r, tbl-orientation}
#| label: tbl-sides
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_or_res <- data_orient %>%
  mutate(choice_or = ifelse(choice_horizontal == 0, "Vertical", "Horizontal")) %>%
  dplyr::select(trt, choice_horizontal, choice_or) %>%
  group_by(trt) %>% # Group by treatment and test
  summarize(
    Horizontal_Count = sum(choice_or == "Horizontal"),
    Vertical_Count = sum(choice_or == "Vertical")
  ) %>% # Count the number of horizontal and vertical choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = Horizontal_Count + Vertical_Count,  # Calculate total choices
    p_value = format_dec(binom.test(Horizontal_Count, total_choices)$p.value, 3)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(trt = recode(trt, 
            "B_23" = "CORT-Cold (n = 20)", 
            "A_23" = "Control-Cold (n = 20)", 
            "B_28" = "CORT-Hot (n = 20)", 
            "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, Horizontal_Count, Vertical_Count, p_value) %>% # Remove unused columns
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
orient_table <- flextable(data_or_res) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("Horizontal"), part = "header") %>%
  compose(j = 3, value = as_paragraph("Vertical"), part = "header") %>%
  compose(j = 4, value = as_paragraph("p-value"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
orient_table
```
